quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-04 paper-quollr.Rmd
Updated the limit

The generated p-D model, overlaid with the data, can also be visualized using `show_langevitour`. Additionally, it features a function for visualizing the $2\text{-}D$ projection of the fitted model overlaid on the data, called `plot_proj`.

@@

nldr4 <- trimap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("d")

@@

error_plot_limb <- plot_rmse(error_limb) +
  scale_x_continuous(breaks = sort(unique(error_limb$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#999999','#a65628','#e41a1c','#377eb8','#4daf4a','#ff7f00','#984ea3','#f781bf'))

@@

tsne_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb, 
  b1 = 19, 
  q = 0.1, 
  benchmark_highdens = 5)

@@

tsne_best_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb2, 
  b1 = 19, 
  q = 0.1, 
  benchmark_highdens = 1)

>>>>

The generated $p\text{-}D$ model, overlaid with the data, can also be visualized using `show_langevitour`. Additionally, it features a function for visualizing the $2\text{-}D$ projection of the fitted model overlaid on the data, called `plot_proj`.

@@

nldr4 <- trimap_limb |>
  ggplot(aes(x = emb1,
             y = emb2)) +
  geom_point(alpha=0.1, size=1, colour='#984ea3') +
  interior_annotation("d")

@@

error_plot_limb <- plot_rmse(error_limb) +
  scale_x_continuous(breaks = sort(unique(error_limb$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#999999','#a65628','#e41a1c','#984ea3','#4daf4a','#ff7f00'))

@@

tsne_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb, 
  b1 = 19, 
  q = 0.1, 
  benchmark_highdens = 0)

@@

tsne_best_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb2, 
  b1 = 19, 
  q = 0.1, 
  benchmark_highdens = 0)
